# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r, echo = TRUE}
dcsv<-read.csv('activity.csv', header = TRUE)
library(data.table)
dtable<-data.table(dcsv)
```
## What is mean total number of steps taken per day?

```{r,echo = TRUE}
dtsum<-dtable[, sum(steps), by=date]
dtsum[,V1]
hist(dtsum[,V1])
```

### mean
```{r, echo = TRUE}
mean(dtsum[,V1],na.rm=TRUE)
```
### median
```{r,echo=TRUE}
median(dtsum[,V1],na.rm=TRUE)
```
## What is the average daily activity pattern?

### plot by interval

```{r,echo=TRUE}
dtmean<-dtable[,mean(steps,na.rm = TRUE),by = interval]
plot(dtmean,type= "l")
```

### Interval with max steps
```{r,echo = TRUE}
dtmean[(dtmean[,V1]==max(dtmean[,V1]))==TRUE][,interval]
```

## Imputing missing values

### Number of missing values
```{r,echo=TRUE}
sum(is.na(dtable[,steps]) == TRUE)
```

### Filling missing values by average of intervals by all days

```{r,echo=TRUE}
#dtmean[dtmean[,interval == 5]][,V1]
#dtable[dtable[,interval == 5]]

Dtable<-transform(dtable,steps = as.double(steps),date = as.Date(date))
dtable2<-Dtable

sapply(Dtable,mode)

for(i in dtmean[,interval])
  {
  dt_intl<-Dtable[Dtable[,interval == i]]
  dt_intl_cond<-is.na(dt_intl[,steps]) == TRUE
  #Dt_intl<-transform(dt_intl,steps=as.double(steps))
  fill<-as.double(dtmean[dtmean[,interval == i]][,V1])
  #print(fill)
  dtable2[dtable2[,interval == i]][dt_intl_cond][,"steps"] <- as.double(fill)
  
  }

sum(is.na(dtable2[,steps]))
```

### histogram of dataset with no missing values
```{r, echo=TRUE}

dtsum2<-dtable2[, sum(steps), by=date]
#dtsum2[,V1]
hist(dtsum2[,V1])
dtable2
dtable

```
## Are there differences in activity patterns between weekdays and weekends?
```{r,echo=TRUE}
dtable2[,weekdays:=1]
dtable2[weekdays(dtable2[,date]) == "Sunday"][,"weekdays"] = 2
dtable2[weekdays(dtable2[,date]) == "Sunday"]

dtable2_wy<-dtable2[dtable2[,weekdays] == 1]
dtable2_wd<-dtable2[dtable2[,weekdays] == 2]

dtmean_wy<-dtable2_wy[,mean(steps),by = interval]
dtmean_wd<-dtable2_wd[,mean(steps),by = interval]

par(mfrow=c(2,1))
plot(dtmean_wy,type= "l")
title("weekdays")
plot(dtmean_wd,type= "l")
title("weekend")

```
